---
title: "Pedestrian Data Analysis"
author: "Power In Numbers: Ken Furushima"
#date: "6/30/2019"
header-includes:
  - \usepackage{ctex}
output:
  #word_document:
  #  df_print: paged
  #  toc: yes
  #  fig_width: 6 
  #  fig_height: 2.5
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  #pdf_document:
  #  toc: true
  #  #toc_depth: 2
  #  fig_caption: true
  #  fig_width: 6
  #  fig_height: 3
  #  latex_engine: xelatex
editor_options:
  chunk_output_type: inline
---


```{r results="hide", echo = FALSE, include=FALSE}
library(tidyverse)
#library(plyr)
library(readxl)
#library(knitr)
#library(kableExtra)
library(ggmap)
library(maps)
library(mapdata)
# load libraries
library(raster)
library(rgdal)
library(broom)
library(RColorBrewer)
library(rgeos)
# note that you don't need to call maptools to run the code below but it needs to be installed.
library(maptools)
# to add a north arrow and a scale bar to the map
library(ggsn)
library(OpenStreetMap)
library(gganimate)
library(gifski)
install.packages(ggplot)
#https://www.linkedin.com/pulse/plot-over-openstreetmap-ggplot2-abel-tortosa-andreu/
Folder <- "E:/Analysis/Pedestrian Data/"
URL <- paste0("https://www.hotcity.co.nz",
              readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts")[
                readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts") %>%
                  grep(".xlsx",.) %>% max()] %>% 
                substr(., regexpr("/sites", .), regexpr("\">", .)-1)
)
FileName <- paste("All pedestrian data day by hour ",
                  readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts")[
                    readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts") %>%
                      grep("data to",.) %>% min()
                    ] %>% 
                    substr(., regexpr("data to", .)+5, regexpr("</a>", .)-1) %>% 
                    gsub("&nbsp;", " ", .),
                  ".xlsx",
                  sep = ""
)
#setwd(Folder)
#download.file(URL, FileName) 
LatestData <- read_xlsx("C:/Users/kfur006/Desktop/Random Data/Pedestrian/All pedestrian data day by hour to 30 June 2019.xlsx",
                        #paste("E:/Analysis/Pedestrian Data/", FileName, sep = ""),
                        sheet = 1) %>% 
  filter(!is.na(`Te Ara Tahuhu Walkway`)) %>%
  #select(-`107 Quay Street`) %>% 
  gather(., Address, Value, -c(Date, Time)) %>% 
  left_join(.,
            read_xlsx("C:/Users/kfur006/Desktop/Random Data/Pedestrian/Pedestrian Geodata.xlsx", sheet = 1)
            #read_xlsx("E:/Analysis/Pedestrian Data/Pedestrian Geodata.xlsx", sheet = 1),
  ) %>% 
  mutate(Months = months(Date),
         Day = factor(weekdays(Date), levels = c("Monday",
                                                 "Tuesday",
                                                 "Wednesday",
                                                 "Thursday",
                                                 "Friday",
                                                 "Saturday",
                                                 "Sunday")),
         Time_Hour = as.numeric(if_else(substr(Time, 2, 2)==":", substr(Time, 1, 1), substr(Time, 1, 2))),
         )
head(LatestData)

  
LatestDataMeanbyDay <- LatestData %>% 
  group_by(Day, Time, Address, Latitude, Longitude, Time_Hour) %>% 
  summarise(Mean = round(mean(Value),0))

StreetData <- read.csv("E:/Analysis/Pedestrian Data/nz-street-address.csv",
                       header = T) %>%
  dplyr::select(gd2000_xcoord, gd2000_ycoord, suburb_locality, town_city) %>% 
  unique() %>% 
  #filter(gd2000_xcoord %inrange% c(min(LatestData$Longitude):max(LatestData$Longitude)),
  #         gd2000_ycoord %inrange% c(min(LatestData$Latitude):max(LatestData$Latitude)),
  filter(gd2000_xcoord >= min(LatestData$Longitude) & gd2000_xcoord <= max(LatestData$Longitude) &
           gd2000_ycoord >= min(LatestData$Latitude) & gd2000_ycoord <= max(LatestData$Latitude)
  )
names(StreetData)
filter(x %in% (3:7))
?geom_map
ggplot() + geom_map(data=LatestDataMeanbyDay, map=skorea, 
                    aes(x=long, y=lat, map_id=id, group=group),
                    fill=NA, color="black")
LatestDataMeanbyDay %>% 
  filter(Day == "Friday",
         Time == "0:00--:59") %>% 
  ggplot(data = .) + geom_polygon( aes(x = Longitude, y = Latitude, group = Day)) + 
  coord_fixed(1.3)
nz <- map_data("nz")
map('nz',
    xlim = c(floor(min(LatestDataMeanbyDay$Longitude)), ceiling(min(LatestDataMeanbyDay$Longitude))),
    ylim = c(floor(min(LatestDataMeanbyDay$Latitude)), ceiling(max(LatestDataMeanbyDay$Latitude))))
# Prepare a map of NZ
nzmap <- ggplot(nz, aes(x = long, y = lat, group = group)) +
  geom_polygon(fill = "white", colour = "black") +
  coord_map()
ggplot() +
  geom_point(data = StreetData, aes(x = gd2000_xcoord, y = gd2000_ycoord, group = town_city)) +
  labs(title = "ggplot map of roads") 
StreetData[order(StreetData$gd2000_xcoord,
                 StreetData$gd2000_ycoord),] %>% 
  ggplot(data = .) + 
  geom_polygon(aes(x = gd2000_xcoord, y = gd2000_ycoord, group = town_city), fill = NA, color = "red") + 
  coord_fixed(1.3)




LAT1 = min(LatestDataMeanbyDay$Latitude) - 0.001 ; LAT2 = max(LatestDataMeanbyDay$Latitude) + 0.002
LON1 = min(LatestDataMeanbyDay$Longitude) - 0.001 ; LON2 = max(LatestDataMeanbyDay$Longitude) + 0.001


map <- openmap(c(LAT2,LON1), c(LAT1,LON2), zoom = NULL,
               type = c("osm", "stamen-toner", "stamen-terrain","stamen-watercolor", "esri","esri-topo")[6],
               mergeTiles = TRUE)

map.latlon <- openproj(map, projection = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
p <- autoplot(map.latlon) +
  geom_point(data = LatestDataMeanbyDay %>% ungroup() %>% mutate(Day_Time = paste(Day, Time)),
             aes(x=Longitude, y=Latitude, fill=Day, size=Mean), shape=21)

?POSIXct
unique(LatestDataMeanbyDay$Day)
unique(LatestDataMeanbyDay$Time)

paste(LatestDataMeanbyDay$Day, LatestDataMeanbyDay$Time)
strptime(x, "%m/%d/%y %H:%M:%S")

thedate = ISOdate(2005,10,21,18,47,22,tz="PDT")
format(thedate,'%A, %B %d, %Y %H:%M:%S')
] "Friday, October 21, 2005 18:47:22"

p +
  facet_wrap(~Day) +
  transition_time(Time_Hour) +
  labs(title = "Time: {frame_time}")

```


# Data Source
The data is from [Heart of the City Incorporated](https://www.hotcity.co.nz/) under [Pedestrian counts](https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts).
The data updates Monthly data is updated by the 7th of each month.
Road data is from [data.linz](https://data.linz.govt.nz/layer/53353-nz-street-address/data/)


```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
