---
title: "Pedestrian Data Analysis"
author: "Power In Numbers: Ken Furushima"
#date: "6/30/2019"
header-includes:
  - \usepackage{ctex}
output:
  #word_document:
  #  df_print: paged
  #  toc: yes
  #  fig_width: 6 
  #  fig_height: 2.5
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  #pdf_document:
  #  toc: true
  #  #toc_depth: 2
  #  fig_caption: true
  #  fig_width: 6
  #  fig_height: 3
  #  latex_engine: xelatex
editor_options:
  chunk_output_type: inline
---


```{r results="hide", echo = FALSE, include=FALSE}
library(tidyverse)
#library(plyr)
library(readxl)
#library(knitr)
#library(kableExtra)
library(ggmap)
library(maps)
library(mapdata)
# load libraries
library(raster)
library(rgdal)
library(broom)
library(RColorBrewer)
library(rgeos)
# note that you don't need to call maptools to run the code below but it needs to be installed.
library(maptools)
# to add a north arrow and a scale bar to the map
library(ggsn)

Folder <- "E:/Analysis/Pedestrian Data/"
URL <- paste0("https://www.hotcity.co.nz",
              readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts")[
                readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts") %>%
                  grep(".xlsx",.) %>% max()] %>% 
                substr(., regexpr("/sites", .), regexpr("\">", .)-1)
)

FileName <- paste("All pedestrian data day by hour ",
      readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts")[
        readLines("https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts") %>%
          grep("data to",.) %>% min()
        ] %>% 
        substr(., regexpr("data to", .)+5, regexpr("</a>", .)-1) %>% 
        gsub("&nbsp;", " ", .),
      ".xlsx",
      sep = ""
)
#setwd(Folder)

#download.file(URL, FileName) 


LatestData <- read_xlsx(paste("E:/Analysis/Pedestrian Data/", FileName, sep = ""),
                        sheet = 1) %>% 
  filter(!is.na(`Te Ara Tahuhu Walkway`)) %>%
  select(-`107 Quay Street`) %>% 
  gather(., Address, Value, -c(Date, Time)) %>% 
  left_join(.,
            read_xlsx("E:/Analysis/Pedestrian Data/Pedestrian Geodata.xlsx", sheet = 1),
  ) %>% 
  mutate(Months = months(Date),
         Day = weekdays(Date))

LatestDataMeanbyDay <- LatestData %>% 
  group_by(Day, Time, Address, Latitude, Longitude) %>% 
  summarise(Mean = round(mean(Value),0))


StreetData <- read.csv("E:/Analysis/Pedestrian Data/nz-street-address.csv",
                       header = T) %>%
  dplyr::select(gd2000_xcoord, gd2000_ycoord, suburb_locality, town_city) %>% 
  unique() %>% 
  #filter(gd2000_xcoord %inrange% c(min(LatestData$Longitude):max(LatestData$Longitude)),
  #         gd2000_ycoord %inrange% c(min(LatestData$Latitude):max(LatestData$Latitude)),
  filter(gd2000_xcoord >= min(LatestData$Longitude) & gd2000_xcoord <= max(LatestData$Longitude) &
           gd2000_ycoord >= min(LatestData$Latitude) & gd2000_ycoord <= max(LatestData$Latitude)
  )
names(StreetData)
filter(x %in% (3:7))

?geom_map
ggplot() + geom_map(data=LatestDataMeanbyDay, map=skorea, 
                    aes(x=long, y=lat, map_id=id, group=group),
                    fill=NA, color="black")

LatestDataMeanbyDay %>% 
  filter(Day == "Friday",
         Time == "0:00--:59") %>% 
  ggplot(data = .) + geom_polygon( aes(x = Longitude, y = Latitude, group = Day)) + 
  coord_fixed(1.3)

nz <- map_data("nz")

map('nz',
    xlim = c(floor(min(LatestDataMeanbyDay$Longitude)), ceiling(min(LatestDataMeanbyDay$Longitude))),
    ylim = c(floor(min(LatestDataMeanbyDay$Latitude)), ceiling(max(LatestDataMeanbyDay$Latitude))))


# Prepare a map of NZ
nzmap <- ggplot(nz, aes(x = long, y = lat, group = group)) +
  geom_polygon(fill = "white", colour = "black") +
  coord_map()


ggplot() +
  geom_point(data = StreetData, aes(x = gd2000_xcoord, y = gd2000_ycoord, group = town_city)) +
  labs(title = "ggplot map of roads") 

StreetData[order(StreetData$gd2000_xcoord,
                 StreetData$gd2000_ycoord),] %>% 
ggplot(data = .) + 
  geom_polygon(aes(x = gd2000_xcoord, y = gd2000_ycoord, group = town_city), fill = NA, color = "red") + 
  coord_fixed(1.3)



```


# Data Source
The data is from [Heart of the City Incorporated](https://www.hotcity.co.nz/) under [Pedestrian counts](https://www.hotcity.co.nz/city-centre/results-and-statistics/pedestrian-counts).
The data updates Monthly data is updated by the 7th of each month.
Road data is from [data.linz](https://data.linz.govt.nz/layer/53353-nz-street-address/data/)


```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.